### 2024-01-01 thesis/chapters/04-implementation.tex
Fix grammar

\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}). Altogether two units are available in two independent air conditioning units for the data center. The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz). Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll. Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.

@@

The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}). The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz). The electric motor provides 400~kW of power (class~\rom{3}). Outer bearing on pump vibrates with acceleration of $\pm 5 \;\mathrm{m/s}^2$.

@@

\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}. In addition, we are able to export the entire historical record in hourly intervals. Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps  (Figure~\ref{fig:design:ksb-guard}).

\section{Sensor hardware and drivers}
In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller. The bandwidth, sensitivity, and sampling frequency of the makeshift solution are not appear to be adequate (Table~\ref{tab:design:hw-sensors}).

@@

The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring. An interface capable of higher speeds is needed to store all acceleration samples. Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus. The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pins. The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.

@@

\section{Preliminary measurements}
During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g.

In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned, below the resonance frequency of the accelerometer (550 Hz). The compressor suspected to be faulty has stronger \nth{4} harmonic and above than the other one.

>>>>

\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}). Altogether, two units are available in two independent air conditioning units for the data center. The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz). Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll. Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.

@@

The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}). The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz). The electric motor provides 400~kW of power (class~\rom{3}). The outer bearing on the pump vibrates with an acceleration of $\pm 5 \;\mathrm{m/s}^2$.

@@

\textbf{Complete schedule} for planned vibration data gathering on the designated machines and measurement procedure is described in Appendix~\ref{appendix:technical-docs}. In addition, we are able to export the entire historical record at hourly intervals. Logs from \textbf{KSB Guard} cloud monitoring tool contain vibration rms velocities and frequency spectra for two monitored KSB water pumps (Figure~\ref{fig:design:ksb-guard}).

\section{Sensor hardware and drivers}
In preliminary exploratory vibration measurements of machines, the ADXL335 accelerometer is connected to BeagleBone Black microcontroller. The bandwidth, sensitivity, and sampling frequency of the makeshift solution do not appear to be adequate (Table~\ref{tab:design:hw-sensors}).

@@

The IIS3DWB accelerometer is a cheap enough MEMS accelerometer that approaches industrial standards for vibration monitoring. An interface capable of higher speeds is needed to store all acceleration samples. Therefore, ESP32-PoE-ISO is chosen as a microcontroller development kit because it has an SD card slot connected via SD/MMC bus. The accelerometer uses an SPI bus with a maximum speed of 10 MHz that can be connected to any physical GPIO pin. The block diagram of the designed hardware device is in Figure~\ref{fig:design:block-diagram-hw}.

@@

\section{Preliminary measurements}
During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g.

In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz). The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.

### 2024-01-01 thesis/chapters/05-conclusion.tex
Fix grammar

\chapter{Conclusion} \label{section:conclusion}  
In the thesis we focused on trend indicator selection for inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute 10 features summarizing waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.

@@

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotation can be assigned belatedly or even never. Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

@@

Feature selection methods shall be incorporated into incremental learning. Hyperparameters shall be adjusted, and the balancing method used to increase model performance. The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

>>>>

\chapter{Conclusion} \label{section:conclusion}  
In the thesis we focused on trend indicator selection for an inexpensive industrial condition monitoring solution from vibration signals. The goal is to enable timely fault detection of machinery parts with as little input data as possible. For that purpose, we answer four research questions.

Attributes extracted to describe machine behavior come mainly from descriptive statistics, audio signal processing studies, and vibrodiagnostics technical standards (ISO 20186 and ISO 13343). These formulas compute 10 features summarizing the waveform in the temporal domain and 11 features characterizing spectral density estimation in 3 spatial directions \textbf{(RQ1)}.

@@

The considerable obstacle in an autonomous fault detection system deployment is the availability of labels for target variables. Annotations can be assigned belatedly or even never. Incremental learning kNN model on an unbalanced dataset on the whole feature set achieves at best 90\% accuracy with immediate feedback, 85\% with labels coming in 250 long tumbling windows, and 82\% with just 25\% of observations associated with the label. The comparable model trained in batch reaches an accuracy of 98\% \textbf{(RQ4)}.

@@

Feature selection methods should be incorporated into incremental learning. Hyperparameters shall be adjusted, and the balancing method used to increase model performance. The outlined tasks awaiting completion are planned for the DP~\rom{3} phase.

### 2024-01-01 thesis/chapters/appendix/C-technical-documentation.tex
Fix grammar

\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 

@@

\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT000TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 

@@

The plan was consulted and approved by the machinery owners: VNET~a.s. and Bratislavská vodárenská spoločnosť,~a.s. Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution. Total space requirements for 108 recordings are 990 MiB.

\section{Firmware activities}

Activity diagrams describe three basic actions of firmware for logging accelerometer samples:

>>>>

\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#1\end{tabular}}} & MTRA001AT090TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 

@@

\multirow{6}{*}{\textbf{\begin{tabular}[c]{@{}l@{}}Pump KSB\\ position \#7\end{tabular}}} & MTRA001AT090TN                          & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 & \multicolumn{2}{p{1.2cm}|}{}                 \\ \cline{2-8} 

@@

The plan was consulted and approved by the machinery owners: VNET~a.s. and Bratislavská vodárenská spoločnosť,~a.s. Triaxial recording has a duration 60~s (at $f_s$ = 26.7 kHz) and a 16-bit resolution. The total space requirements for 108 recordings are 990 MiB.

\section{Firmware activities}
Activity diagrams describe three basic actions of firmware for logging accelerometer samples:

### 2024-01-01 thesis/chapters/preliminaries/annotation.tex
Fix grammar

Trend indicators are derived from vibration signals to form summarizing numerical attributes. The similarity of features to a dependent variable describing fault types is assessed with supervised feature selection metrics individually and in the ensemble. The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve data rates of the monitoring solution. The incremental learning model is compared to its batch counterpart when truthful labels are delayed or missing.

Based on the MaFaulDa dataset, classification metrics are evaluated in several scenarios, and lossy compression ratios are expressed. The measurement plan and sensor device are designed to enable collection of novel datasets of machinery behavior for compressors and pumps. The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but also its cause.
\emptypage

>>>>

Trend indicators are derived from vibration signals to form summarizing numerical attributes. The similarity of features to a dependent variable describing fault types is assessed by supervised feature selection metrics individually and in the ensemble. The accuracy of fault detection using the k-nearest neighbor is evaluated on the best feature subsets to conserve data rates of the monitoring solution. The incremental learning model is compared to its batch counterpart when truthful labels are delayed or missing.

Based on the MaFaulDa dataset, classification metrics are evaluated in several scenarios, and lossy compression ratios are expressed. The measurement plan and sensor device are designed to enable collection of novel dataset of machinery behavior for compressors and pumps. The contribution of this work lies in identifying the viability of using a few quantities to describe not just the presence of the machine defect but also its cause.
\emptypage
